Har en persons høyde innvirkning på lønnen?

### 2020-10-09 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
La inn geom_smooth.

```{r}
heightsPosInc <- subset(heights, inntekt < 1000000)
ggplot(heightsPosInc, mapping = aes(x = height_cmInt, y = inntekt)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_boxplot()
```

@@

>>>>

```{r boxplot-høyde-inntekt, echo=FALSE}
heightsPosInc <- subset(heights, inntekt < 1000000)
ggplot(heightsPosInc, mapping = aes(x = height_cmInt, y = inntekt)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_boxplot()
```

@@

```{r geom_smooth, echo=False}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = height_cm, y = inntekt)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')
```
